\documentclass{beamer}

\usepackage[english]{babel}
\usepackage{minted}
\newcommand{\mil}[1]{\mintinline{java}{#1}}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{matrix,backgrounds}
\usepackage{hyperref}

\title[Labels]{JavaFX}
\subtitle{Labels} % (optional)

\author[]{Dalton State College} 

%\institute[Dalton State College]

\date[T. Gonzalez]{T. Gonzalez}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command: 

%\beamerdefaultoverlayspecification{<+->}


\begin{document}

\begin{frame}

	\titlepage
	
\end{frame}

\begin{frame}
    
    \frametitle{\mil{Label}}
    
    A \mil{Label} is a non-editable text control
    
    \bigskip
    
    \mil{Label}s are useful for displaying text that is required to fit within a specific space.
    
    \bigskip
    
   Labels can also contain images.  

\end{frame}
	
\begin{frame}[fragile]

	\frametitle{Label Constructors}
	
    \mil{Label()}  Creates an empty label.
    
    \bigskip
    
    \mil{Label(String text)} Creates a label with supplied text.
    
    \bigskip
    
    \mil{Label(String text, Node graphic)}  Creates a label with supplied text and graphic.
	
\end{frame}

\begin{frame}[fragile]

    \frametitle{Adding Components to a \mil{Pane}}
    
    To add a component to a \mil{Pane} use the following method calls:
    
\begin{minted}[fontsize=\footnotesize]{java}
getChildren().add() 
        
getChildren().addAll() 
\end{minted}

\bigskip

The \mil{getChildren()} method returns a \mil{List}.

\bigskip

The \mil{add()} method can be used to add an element to the end of the \mil{List} or at a specified position.

\bigskip

The \mil{addAll()} method can be used to add multiple elements at once.  The arguments need to be separated by commas in the method call.

\bigskip
   
Use the \mil{remove()} method in a similar manner to remove labels from a container.
\end{frame}

\begin{frame}[fragile]

    \frametitle{Accessing and Changing a Label Object's Text}
    
    Use the \mil{getText()} method to access a \mil{Label} object's text.
    
    \bigskip
    
    Use the \mil{setText()} method to change a \mil{Label} object's text. 
    
\end{frame}

\begin{frame}

    See  LabelExample.java.
    
\end{frame}
\end{document}